Towards a Neural Network model fro Aggregate Computing

### 2021-07-07 article.tex
add requirement for action

%%
%% This command is for the conference information
\conference{Woodstock'20: Symposium on the irreproducible science,
  June 01--05, 2020, Woodstock, NY}

%%
%% The "title" command
\title{A better way to format your document for CEUR-WS}

>>>>

%%
%% This command is for the conference information
\conference{22nd Workshop "From Objects to Agents" 
Bologna, Italy, 1-3 September 2021 }

%%
%% The "title" command
\title{Towards a Neural Network model fro Aggregate Computing}
